New lower bounds for Schur and weak Schur numbers

### 2021-06-07 article/schur.tex
Phrase intro

We define \(S^+\) to reduce the constraints of Abbott and Hanson's construction to improve this construction.

>>>>

We begin by introducing \textit{S-templates}, standing for \textit{"Schur templates"}. The idea is to consider the first line
of Figure 1 not as a combination of two blocs anymore but as a whole, single construction. We thereby define a S-template as
a new object filling the role of the first line but with less, yet sufficiant, constraints that will allow the expansion of the
table.
